Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-11-29 contents/draft.tex
Update minor

    In this study, string alignment was performed using the Smith--Waterman algorithm, which uses a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as shown in Figure~\ref{fig:sample}). Each aligned sentence containing a morpheme tag was converted into a training sample tailored for dictionary-based morphological analysis.

>>>>

    In this study, string alignment was performed using the Smith-Waterman algorithm, which uses a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as shown in Figure~\ref{fig:sample}). Each aligned sentence containing a morpheme tag was converted into a training sample tailored for dictionary-based morphological analysis.
